Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-06-02 Manuscript/00-main.Rmd
Improved the manuscript

```{r plot-ref, fig.cap = "Fancy Caption\\label{fig:plot}"}
x = rnorm(10)
y = rnorm(10)
plot(x, y)
```

@@

```{r, results = "asis"}
if (!require("xtable")) install.packages("xtable")
xt <- xtable(head(cars), caption = "A table", label = "tab:table")
print(xt, comment = FALSE)
```

>>>>

```{r plot-ref, fig.cap = "Fancy Caption\\label{fig:plot}", eval = F}
x = rnorm(10)
y = rnorm(10)
plot(x, y)
```

@@

```{r, results = "asis", eval = F}
if (!require("xtable")) install.packages("xtable")
xt <- xtable(head(cars), caption = "A table", label = "tab:table")
print(xt, comment = FALSE)
```

### 2021-06-02 Manuscript/05-Discussion.Rmd
Improved the manuscript

Remaining issue:
1. Degree of freedom has yet to closely studied. As an direct impact, the functional selection can be improved when effective degree of freedom are more carefully studied
2. Future exapansion, as we were analyzing the metabolites data, we observed that metabolites pathway infromation can be useful in the predictive and integrative model can be developed based on the proposed framework. As an naive solution, the selection indicator of linear effect of the spline terms of all metabolites on the same pathway can be set to share the same hyper prior such that the group selection can be modestly achieved. Meanwhile further advancedment of the methodology regarding to the integrative analysis can consider setting the hypor priors of the selection indivator of the non-linear components conditioning on the probability of inclusion of the linear effect. Such structure is more sensible analytically.

>>>>

Remaining issue:
1. Degree of freedom has yet to closely studied. As an direct impact, the functional selection can be improved when effective degree of freedom are more carefully studied
2. While the proposed model addresses a great deal of analytic problem, analyzing the time-to-event outcome remains unsolved. Our current effort resides on expanding. An naive approach could be convert an time-to-event outcome to a poisson outcome following xxx. Hence, the . However, it would be more efficient to , via penalized pseudo likelihood function, which is the current effort resides.
2. Future exapansion, as we were analyzing the metabolites data, we observed that metabolites pathway infromation can be useful in the predictive and integrative model can be developed based on the proposed framework. As an naive solution, the selection indicator of linear effect of the spline terms of all metabolites on the same pathway can be set to share the same hyper prior such that the group selection can be modestly achieved. Meanwhile further advancedment of the methodology regarding to the integrative analysis can consider setting the hypor priors of the selection indivator of the non-linear components conditioning on the probability of inclusion of the linear effect. Such structure is more sensible analytically.

### 2021-06-02 Manuscript/SS_GAM.tex
Improved the manuscript

\begin{itemize}
\item
  What is the problem

  \begin{itemize}
  \tightlist
  \item
    what is the GAM
  \item
    expanding GAM in to high-dimensional frame work
  \item
    Why this is important
  \item
    Why this is hard
  \end{itemize}
\item
  Previous solutions

  \begin{itemize}
  \tightlist
  \item
    What are the methods
  \item
    What are their problems
  \end{itemize}
\item
  Introduce the wiggliness matrix
\item
  Our method
\item
  The implication of our method
\item
  Fast
\item
  Structure of the rest of the paper
\end{itemize}

@@

Remaining issue: 1. Degree of freedom has yet to closely studied. As an
direct impact, the functional selection can be improved when effective
degree of freedom are more carefully studied 2. Future exapansion, as we
were analyzing the metabolites data, we observed that metabolites
pathway infromation can be useful in the predictive and integrative
model can be developed based on the proposed framework. As an naive
solution, the selection indicator of linear effect of the spline terms
of all metabolites on the same pathway can be set to share the same
hyper prior such that the group selection can be modestly achieved.
Meanwhile further advancedment of the methodology regarding to the
integrative analysis can consider setting the hypor priors of the
selection indivator of the non-linear components conditioning on the
probability of inclusion of the linear effect. Such structure is more
sensible analytically.

\begin{figure}
\centering
\includegraphics{SS_GAM_files/figure-latex/plot-ref-1.pdf}
\caption{Fancy Caption\label{fig:plot}}
\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & speed & dist \\ 
  \hline
1 & 4.00 & 2.00 \\ 
  2 & 4.00 & 10.00 \\ 
  3 & 7.00 & 4.00 \\ 
  4 & 7.00 & 22.00 \\ 
  5 & 8.00 & 16.00 \\ 
  6 & 9.00 & 10.00 \\ 
   \hline
\end{tabular}
\caption{A table} 
\label{tab:table}
\end{table}

>>>>

@@

Remaining issue: 1. Degree of freedom has yet to closely studied. As an
direct impact, the functional selection can be improved when effective
degree of freedom are more carefully studied 2. While the proposed model
addresses a great deal of analytic problem, analyzing the time-to-event
outcome remains unsolved. Our current effort resides on expanding. An
naive approach could be convert an time-to-event outcome to a poisson
outcome following xxx. Hence, the . However, it would be more efficient
to , via penalized pseudo likelihood function, which is the current
effort resides. 2. Future exapansion, as we were analyzing the
metabolites data, we observed that metabolites pathway infromation can
be useful in the predictive and integrative model can be developed based
on the proposed framework. As an naive solution, the selection indicator
of linear effect of the spline terms of all metabolites on the same
pathway can be set to share the same hyper prior such that the group
selection can be modestly achieved. Meanwhile further advancedment of
the methodology regarding to the integrative analysis can consider
setting the hypor priors of the selection indivator of the non-linear
components conditioning on the probability of inclusion of the linear
effect. Such structure is more sensible analytically.

@@
